Self Regulation Ontology Retest Analyses

### 2018-05-14 code/SRO_Retest_Analyses.Rmd
frisem prep

```{r}
boot_df %>%
  select(dv, p_time, task) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect) %>%
  ungroup()%>%
  group_by(task) %>%
  summarise(count=n()) %>%
  mutate(total_num_vars = c(74, 372),
         prop = count/total_num_vars) %>%
  ggplot(aes(task, prop, fill=task))+
  geom_bar(stat="identity", alpha=0.5, width=0.5)+
  theme(legend.position = "none", 
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  ylab("Proportiono of samples")+
  xlab("")

@@

mean_diff_df

# write.csv(mean_diff_df, '/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/mean_diff_df.csv')
```

@@

```{r warning=FALSE, message=FALSE}
mean_diff_df = read.csv('/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/mean_diff_df.csv')

table(as.character(mean_diff_df$valence), useNA = "ifany")

mean_diff_df %>%
  mutate(sc_increase = ifelse(prop_one_direction>0&valence=="Pos",1,ifelse(prop_one_direction<0&valence=="Neg",1,0)),
         sc_decrease = ifelse(prop_one_direction>0&valence=="Neg",1,ifelse(prop_one_direction<0&valence=="Pos",1,0))) %>%
summarise(sum_sc_increase = sum(sc_increase,na.rm=T),
          sum_sc_decrease = sum(sc_decrease,na.rm=T))

@@

```{r}
chisq.test(matrix(data = c(5,74-5,61,372-61), nrow=2))
```

>>>>

```{r}
boot_df %>%
  select(dv, p_time, task) %>%
  mutate(time_effect_sig = ifelse(p_time<0.05,1,0)) %>%
  group_by(dv)%>%
  summarise(pct_sig_time_effect = sum(time_effect_sig)/10,
            task = unique(task))%>%
  filter(pct_sig_time_effect>5) %>%
  arrange(task,-pct_sig_time_effect) %>%
  ungroup()%>%
  group_by(task) %>%
  summarise(count=n()) %>%
  mutate(total_num_vars = c(74, 372),
         prop = count/total_num_vars) %>%
  ggplot(aes(task, prop, fill=task))+
  geom_bar(stat="identity", alpha=0.5, width=0.5)+
  theme(legend.position = "none", 
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  ylab("Proportiono of samples")+
  xlab("")+
  ylim(0,1)

@@

mean_diff_df
```

@@

```{r}
valence_df = read.csv(paste0(retest_data_path, 'DV_valence.csv'), header = F)
valence_df = valence_df %>% rename(dv = V1, valence = V2)
valence_df$task = 'task'
valence_df[grep('survey', valence_df$dv), 'task'] = 'survey'
valence_df[grep('holt', valence_df$dv), 'task'] = "task"

valence_df = valence_df %>% filter(dv %in% retest_report_vars)
with(valence_df, table(task, valence))
#Comparable level of valences for task and survey measures
chisq.test(with(valence_df, table(task, valence)))
```

```{r warning=FALSE, message=FALSE}

mean_diff_df %>%
  left_join(valence_df, by = c("dv", "task")) %>%
  mutate(sc_increase = ifelse(prop_one_direction>0&valence==1,1,ifelse(prop_one_direction<0&valence==-1,1,0)),
         sc_decrease = ifelse(prop_one_direction>0&valence==-1,1,ifelse(prop_one_direction<0&valence==1,1,0))) %>%
  group_by(task) %>%
summarise(sum_sc_increase = sum(sc_increase,na.rm=T),
          sum_sc_decrease = sum(sc_decrease,na.rm=T)) %>%
  gather(key, value, -task) %>%
  mutate(total_vars = c(74, 372, 74, 372),
         prop = value/total_vars) %>%
  ggplot(aes(key, prop, group=task, fill=task))+
  geom_bar(stat = "identity", position = position_dodge(), alpha = 0.5)+
  theme(legend.title = element_blank())+
  xlab("")+
  ylab("Proportion")+
  ylim(0, 1)+
  scale_x_discrete(breaks = c("sum_sc_decrease", "sum_sc_increase"),
                   labels = c("Self-control decrease", "Self-control increase"))

ggsave('PropTimeEffectsValence.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 5, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

@@

```{r}
chisq.test(matrix(data = c(5,74-5,60,372-60), nrow=2))
```
